% @me reminder: overleaf comments
% ragged2e
\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\name{Konstantin}{Sewina}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{ Site Reliability Engineer}\end{center}
\begin{center}
\begin{tabular}{ c c c }
\faEnvelope\enspace konstantin.sewina(at)gmail.com & \faHome\enspace Hof, DE \\
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/konstantin-sewina-319553259/}{in/konstantin-sewina} &
\faGithub\enspace \color{blue} \href{https://github.com/ksewina}{github.com/ksewina}
\end{tabular}
\end{center}

\section{Profile}
{Certified Kubernetes Administrator with 4+ years of experience in the infrastructure side of migrating and developing container-based applications. Skilled in creating and optimizing Kubernetes-based environments, adhering to GitOps best practices with a strong emphasis on reproducibility. Known for innovative problem-solving abilities and consistently seeking out new ideas to improve system efficiency and reliability. Adept at leveraging cutting-edge cloud technologies to deliver robust and scalable solutions. Since this question will come up anyway, I took a long sabatical in 2024 and it was \textbf{awesome}, now I can focus on work again.}

\section{Professional Experience}
\customcventry{06/2022 ‐ 02/2024}{{\color{blue}\href{https://www.gfk.com}{(GfK SE)}}}{Junior Site Reliability Engineer,}{Nuremberg, BY}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Collaborated in a mutli-tenant Kubernetes environment following GitOps best practices to improve stability and scaling. Most proud of adopting event-driven autoscaling in a production environment using KEDA to reduce resource waste and cost of ML applications.
\item Migration and development of python, java(gradle) pipelines from Atlassian Bamboo to Gitlab CI.
\item Prepared and migrated production workloads from Hashicorp Nomad system to Kubernetes.
\item Developed and implemented a Prometheus metric exporter for a proprietary on-premise S3 system in Golang.
\item Mentoring of new joiners
\item Improvements to the Observability stack of Prometheus, Grafana, OpenSearch to have monitoring with actionable alerts.
\item PoC for domain-wide adoption of the RabbitMQ Operator / Topology Message Operator to streamline operational effort and have LessOps.
\end{itemize}}}

\customcventry{01/2023 ‐ 05/2023}{{\color{blue}\href{https://www.google.com/}{(HFO Technology GmbH)}}}{IT Operator,}{Hof, BY}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Implemented promotional activities such as re-targeting campaigns for e-commerce businesses.
\item Monitored the performance of PPC campaigns through Google Adwords. 
\item Managed and optimized PPC campaigns, resulting in a 5\% increase in click-through rates
\end{itemize}}}

\customcventry{03/2023 ‐ 12/2023}{{\color{blue}\href{https://www.google.com/}{(HFO Telecom GmbH)}}}{2nd Level Technical Support,}{Hof, BY}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Identified and executed improvements for processes, content, and lead generation.
\item Collaborated with Content Team to promote blog posts and guest posts.
\item Implemented new competitive analysis and consumer trend reports to increase quarterly sales by 15%.
\end{itemize}}}

\customcventry{01/2022 ‐ 07/2022}{{\color{blue}\href{https://www.google.com/}{(HFO Telecom GmbH)}}}{,}{Hof, BY}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Identified new autoposting solution to cut social media time spent by 35%.
\item Prepared written text proposals and speech writing drafts.
\item Managed all public social media profiles of important public figure.
\end{itemize}}}

\section{Online Courses \& Certifications}
{\begin{itemize}[label=\textbullet]
      \item Linux Foundation: Certified Kubernetes Administrator (Sep. 2022) - \underline{\color{blue}\href{https://www.credly.com/badges/4675ad1e-9857-4791-b7b7-3b85797f0ba4/public_url}{Credly}}
      \item HashiCorp Certified: Terraform Associate (Jan. 2022) - \underline{\color{blue}\href{https://www.pluralsight.com/paths/hashicorp-certified-terraform-associate}{Pluralsight}}
      \item Cilium Platform Engineer Path (ongoing) - \underline{\color{blue}\href{https://isovalent.com/labs/discovery-platform-engineer/}{Isovalent}}
        \item various Udemy courses for anything im interesting in (2017 - forever) - \underline{\color{blue}\href{https://www.udemy.com/user/konstantin-sewina/}{Udemy Profile}}
  \end{itemize}} 

\section{Education}
\customcventry{2014-2017}{\color{blue}\href{https://www.bsz-eoplauen.de/}{BSZ e.o.plauen}}{IT Specialist - Systems Integration}{Plauen, Saxony}{}{}
\customcventry{graduated 2014}{\color{blue}\href{https://www.mosengymnasium.de/}{Julius-Mosen-Gynmnasium}}{High School Diploma}{Oelsnitz, Saxony}{}{}

\section{Skills}
{\begin{itemize}[label=\textbullet]
\item {\textbf{Cloud Providers:} AWS, GCP, Hetzner}
\item {\textbf{Scheduling \& Orchestration:} Kubernetes, Docker, KEDA}
\item {\textbf{Infrastructure \& Services:} FluxCD, Helm, Kustomize, Terraform, RabbitMQ, Postgres}
\item {\textbf{Observability:} Prometheus, fluentd/fluentbit, Grafana, Loki, OpenSearch, eBPF-based}
\item {\textbf{General Toolbelt:} Git, Gitlab CI, Linux, bash, vim}
\item {\textbf{Programming Languages:} Golang}
\end{itemize}}

\section{Languages}
\begin{multicols}{2}
    \begin{itemize}[label=\textbullet]
    \item \textbf{German} [Native]
    \item {\textbf{English} [C1]}
    \item {\textbf{French} [A2]}
    \end{itemize}
\end{multicols}
\end{document}